\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
        \resumeProjectHeading
        {\textbf{NFS Most Wanted Self-Driving Car with OpenCV and TensorFlow} $|$ \emph{OpenCV, TensorFlow}}{2022}
        \resumeItemListStart
            \resumeItem{Developed a self-driving car system within the NFS Most Wanted environment using computer vision algorithms to detect lines and lanes for navigation.}
            \resumeItem{Implemented object detection techniques to identify and track vehicles and pedestrians, enhancing safety and maneuverability.}
        \resumeItemListEnd

        \resumeProjectHeading
        {\textbf{Fairfield Wildlife Surveillance} $|$ \emph{YOLOv8, Raspberry Pi4, RoboFlow}}{2023}
        \resumeItemListStart
            \resumeItem{Conceptualized and implemented the project's architecture, achieving a 95\% F1 score with the YOLOv8 object detection model.}
            \resumeItem{Developed a website allowing users to select animal classes for recording and adjust confidence thresholds for detection, integrating seamlessly with the surveillance system.}
        \resumeItemListEnd

        \resumeProjectHeading
        {\textbf{Raspberry Pi-based Wild Boar Detection and Deterrence System for Corn Fields} $|$ \emph{Raspberry Pi4, YOLO5, OpenCV}}{2022}
        \resumeItemListStart
            \resumeItem{Developed a rapid object detection model based on YOLO5 trained on wild boar images to protect crops from wildlife threats.}
            \resumeItem{Implemented a responsive system that captures videos and sends alerts upon detection, effectively safeguarding agricultural fields.}
        \resumeItemListEnd

        \resumeProjectHeading
        {\textbf{Image Stitching with OpenCV - C++ | GitHub} $|$ \emph{C++, OpenCV}}{2021}
        \resumeItemListStart
            \resumeItem{Conducted image stitching operations using C++ and OpenCV, developing a robust system for creating cohesive panoramas from multiple images.}
            \resumeItem{Utilized keypoint and feature-based techniques to achieve high-quality stitching results, enhancing the versatility of the system for various applications.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd